### 2016-09-27 2nd_round_comments/DVCS-CAN-Meeting-Comments.tex
updating the plots for the second round comments

  \item Produce all 9 plots in right figure of slides 5 and 9 of \url{ 
     https://clasweb.jlab.org/rungroups/lowq/wiki/images/a/a0/ExcluCuts-CANeg6.pdf}   
     for a 2$\sigma$ and 1$\sigma$ cuts on missing $ep\gamma X$ M2.\\
     \textcolor{blue}{The coherent and the incoherent distributions are 
        presented in figure \ref{fig:exc_Coh} and \ref{fig:exc_InCoh} 
     respectively. The reconstructed coherent and incoherent beam spin 
  asymmetries are presented in figures \ref{fig:exc_coh-alu} and 
  \ref{fig:exc_incoh-alu} respectively. In terms of the exclusivity 
  distributions, no correlations were observed in the coherent DVCS channel, 
  while a slight correlation was observed between the $ep\gamma$ MM2 and $epX$ 
  MM2.} \textcolor{red}{Do we have to apply tighter cuts in the incoherent 
  case?.}

@@

\item Free proton asymmetries from FX's publication: implement a (possibly 3D/9 
points) interpolation to smooth out both statistical fluctuations and 
kinematical dependences. Reintroduce a corresponding section in the CAN. Take 
into account both stat. and syst. errors of both experiments in the ratio. The 
committee recommends though to be cautious about the statements on the 
asymmetry ratios in the future publication.\\
  \textcolor{blue}{We changed the procedures completely, see Appendix G in the 
  latest version of the analysis note. We performed fittings for the published 
  free proton asymmetries. Then we used those fits to extrapolate the free 
  proton asymmetries at our measured kinematics}.\\
  \begin{figure}[tbp]
    \includegraphics[height=14.6cm]{fig/ALU-proton-fits.png}
    \caption{ Fitting e1dvcs1 free proton beam-spin asymmetries. The dashed 
    curves are fits to the data in the form of 
 $p_{0}*(t-t_{min})*e^{p_{1}*\sqrt{t}}$, while the solid curves are from 
 calculations based on fitting the parameters $p_{0}$ and $p_{1}$.}
    \label{fig:free-proton-alu-fits}
    \end{figure}

  \begin{figure}[tbp]
    \includegraphics[height=6.6cm]{fig/BSA_ratio_coh_Q2.pdf}
    \includegraphics[height=6.6cm]{fig/BSA_ratio_coh_x.pdf}
    \centering
    \includegraphics[height=6.6cm]{fig/BSA_ratio_coh_t.pdf}
    \caption{ $A_{LU}$ ratio between $^{4}$He DVCS and free proton at $\phi = 
    90 ^{\circ}$ as a function of $Q^{2}$, $x_{B}$, and $-t$.}
    \label{fig:coh-alu-ratios}
    \end{figure}

 \begin{figure}[tbp]
    \includegraphics[height=6.6cm]{fig/BSA_ratio_incoh_Q2.pdf}
    \includegraphics[height=6.6cm]{fig/BSA_ratio_incoh_x.pdf}
    \centering
    \includegraphics[height=6.6cm]{fig/BSA_ratio_incoh_t.pdf}
    \caption{ $A_{LU}$ ratio between bound proton and free proton at $\phi =  
    90 ^{\circ}$ as a function of $Q^{2}$, $x_{B}$, and $-t$.}
    \label{fig:incoh-alu-ratios}
    \end{figure}

>>>>

  \item Produce all 9 plots in right figure of slides 5 and 9 of \url{ 
     https://clasweb.jlab.org/rungroups/lowq/wiki/images/a/a0/ExcluCuts-CANeg6.pdf}   
     for a 2$\sigma$ and 1$\sigma$ cuts on missing $ep\gamma X$ M2.\\
     \textcolor{blue}{The coherent and the incoherent distributions are 
        presented in figure \ref{fig:exc_Coh} and \ref{fig:exc_InCoh} 
     respectively. The reconstructed coherent and incoherent beam spin 
  asymmetries are presented in figures \ref{fig:exc_coh-alu} and 
  \ref{fig:exc_incoh-alu} respectively. In terms of the exclusivity 
  distributions, no correlations were observed in the coherent DVCS channel, 
  while a slight correlation was observed between the $ep\gamma$ MM2 and $epX$ 
  MM2.}

@@

\item Free proton asymmetries from FX's publication: implement a (possibly 3D/9 
points) interpolation to smooth out both statistical fluctuations and 
kinematical dependences. Reintroduce a corresponding section in the CAN. Take 
into account both stat. and syst. errors of both experiments in the ratio. The 
committee recommends though to be cautious about the statements on the 
asymmetry ratios in the future publication.\\
  \textcolor{blue}{We changed the procedures completely, see Appendix G in the 
  latest version of the analysis note. We performed fittings for the published 
  free proton asymmetries. Then we used those fits to extrapolate the free 
  proton asymmetries at our measured kinematics}.\\
  \begin{figure}[tbp]
    \includegraphics[height=14.6cm]{fig/ALU-proton-fits.pdf}
    \caption{Black circles are the free proton beam-spin asymmetries at $\phi = 
    90   ^{\circ}$ as a function of $-t$ in different ($x_B, Q^2$) bins as 
    measured at CLAS-E1DVCS experiment. The solid red curves are fits to the 
    free proton asymmetries in the form 
    $a_{0}*(\sqrt{t}-a_{1})*e^{a_{2}*\sqrt{t} - a_{3}}$. The dashed curves are 
    calculations using the fitted $a_{i}$'s parameters as
 a function of $x_B$. Blue points are the interpolated points corresponding for 
 the incoherent points presented
 in this analysis. The red points stand for the extrapolated free proton
 asymmetries at the measured coherent kinematics.}
    \label{fig:free-proton-alu-fits}
    \end{figure}

  \begin{figure}[tbp]
    \includegraphics[height=6.6cm]{fig/BSA_ratio_coh_Q2.pdf}
    \includegraphics[height=6.6cm]{fig/BSA_ratio_coh_xB.pdf}
    \centering
    \includegraphics[height=6.6cm]{fig/BSA_ratio_coh_t.pdf}
    \caption{ $A_{LU}$ ratio between $^{4}$He DVCS and free proton at $\phi = 
    90 ^{\circ}$ as a function of $Q^{2}$, $x_{B}$, and $-t$.}
    \label{fig:coh-alu-ratios}
    \end{figure}

 \begin{figure}[tbp]
    \includegraphics[height=6.6cm]{fig/BSA_ratio_incoh_Q2.pdf}
    \includegraphics[height=6.6cm]{fig/BSA_ratio_incoh_xB.pdf}
    \centering
    \includegraphics[height=6.6cm]{fig/BSA_ratio_incoh_t.pdf}
    \caption{ $A_{LU}$ ratio between bound proton and free proton at $\phi =  
    90 ^{\circ}$ as a function of $Q^{2}$, $x_{B}$, and $-t$.}
    \label{fig:incoh-alu-ratios}
    \end{figure}
